---
title: "Discussion 1"
author: "Po"
date: "10/6/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Logistics
Name: Chi Po Choi

Email: `cpchoi@ucdavis.edu` (Email title starts with `[STA137]`, or maybe [piazza](https://piazza.com/class/kfcspxpbyp97gn)?)

Office Hours: Tuesday 12noon-ish ~ 1pm-ish, Thursday 12noon-ish ~ 1pm-ish



# R time series landscape

There are a lots of R functions and R packages for time series analysis.

Time-Series Objects
```{r}
?ts
```

[CRAN Task View: Time Series Analysis](https://cran.r-project.org/web/views/TimeSeries.html)


# Data in textbook

The *Chapman&Hall textbook* **Time Series: A Data Analysis Approach Using R** and the *Springer textbook* **Time Series Analysis and Its Applications** has a companion R package `astsa` which contains time series data illustrated. https://github.com/nickpoison/astsa

Install it and get the data.
```{r, eval=FALSE}
# In case you haven't install devtools
# install.packages("devtools")
devtools::install_github("nickpoison/astsa")
```

For example, `eqexp` is
```{r}
?astsa::eqexp
```
> This is a data frame of the earthquake and explosion seismic series used throughout the text.

```{r}
head(astsa::eqexp)
```

```{r}
str(astsa::eqexp)
```


# Plotting time series

```{r}
p_index = 1:1024
time_series_name = c("EQ6", "EX4")
time_series_to_be_plotted = astsa::eqexp[p_index, time_series_name]
plot.ts(time_series_to_be_plotted,
        plot.type = "multiple",
        nc = 1,
        main = "P waves")
```

```{r}
s_index = p_index+1024
colors_name = c("red", "blue")
time_series_to_be_plotted = astsa::eqexp[s_index, time_series_name]
plot.ts(time_series_to_be_plotted,
        plot.type="single",
        main="S waves",
        col=colors_name,
        ylab="somethings")
legend("bottomleft",
       time_series_name,
       col=colors_name,
       lty=1)
```

Plotting Time-Series Objects
```{r}
?plot.ts
```

R knowledge question: Do you know what are the differences among those calls?

- `plot.ts(x)`
- `plot(ts(x))`
- `plot(x)`
- `plot.ts(ts(x))`


# Simulating time series

$x_t = s_t + \omega_t$ where $\omega_t \sim WN(0,1)$
$$
s_t = 
      \begin{cases}
      0, & t=1,\dots,125 \\
      10\;e^{-\frac{t-125}{25}}\cos(2\pi t/4) ,& t=126,\dots,250
      \end{cases}
$$

```{r}
s_fun = function(t) ifelse(t<=125, 0, 10*exp(-(t-125)/25)*cos(2*pi*t/4))
omega_fun = function(t) rnorm(length(t))

t_index = 1:250
set.seed(19460614)
x = ts(s_fun(t_index) + omega_fun(t_index))
```

```{r}
str(x)
```

```{r}
plot(x)
```

```{r}
acf(x)
```

```{r}
str(acf(x, plot=F))
```

# Summary

- `?`
- `str`
- `ts`
- `plot.ts`
- `acf`
