---
title: "Discussion 2"
author: "Po"
date: "10/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Logistics

[Piazza](https://piazza.com/uc_davis/fall2020/sta137/home)

# Moving average

```{r}
?filter
?acf
```

```{r}
set.seed(530476)
N = 16
w = rnorm(N)
x = filter(w, filter=rep(1/5,5))

some_ts = cbind(w, x)
some_ts
plot(some_ts)
x_acf = acf(x, na.action = na.omit)
```


```{r}
str(acf(x, na.action = na.pass, plot=F))
```
```{r}
str(acf(x, na.action = na.omit, plot=F))
```


```{r}
data.frame(lag = x_acf$lag,
           acf = x_acf$acf)
```

By the way, what is the difference?
- `cbind(x, w)`
- `data.frame(x, w)`
- `ts(data.frame(x, w))`

# Transformation

Sedimentary deposits from one location in Massachusetts for 634 years, beginning nearly 12,000 years ago.
```{r}
?astsa::varve
```

```{r, fig.height=12}
varve_more = cbind(astsa::varve, log(astsa::varve), diff(log(astsa::varve)))
plot(varve_more)
```

```{r}
?log
?diff
```

# Seasonality

Lets look at some built-in datasets in R.
```{r}
library(help = "datasets")
```

For example, Quarterly Approval Ratings of US Presidents
```{r}
presidents
```

```{r}
plot(presidents, main="Quarterly Approval Ratings of US Presidents")
```

For example, Monthly Airline Passenger Numbers 1949-1960
```{r}
AirPassengers
```
```{r, fig.height=8}
plot(cbind(AirPassengers, log10(AirPassengers)),
     main="Monthly Airline Passenger Numbers 1949-1960")
```

```{r}
AirPassengers_df = data.frame(
  p = log10(AirPassengers),
  t = time(AirPassengers),
  m = as.factor(cycle(AirPassengers))
)
head(AirPassengers_df)
```

```{r}
makeDF = function(x) {
  df = data.frame(
    y = log10(x),
    t = time(x),
    s = as.factor(cycle(x))
  )
}
seaLS1 = function(x) {
  df = makeDF(x)
  lm(y ~ t - 1 + s, data = df)
}
seaLS2 = function(x) {
  df = makeDF(x)
  lm(y ~ t + s, data = df)
}
seaLS3 = function(x) {
  df = makeDF(x)
  lm(y ~ t + s, data = df, contrasts = list(s = contr.sum))
}
seaLS4 = function(x) {
  df = makeDF(x)
  lm(y ~ t, data = df)
}

mod1 = seaLS1(AirPassengers)
mod2 = seaLS2(AirPassengers)
mod3 = seaLS3(AirPassengers)
mod4 = seaLS4(AirPassengers)
```

Can you tell the difference between `seaLS1`, `seaLS2`, `seaLS3` and `seaLS4`? (Try `model.matrix(mod1)` etc!)

```{r}
summary(mod1)
summary(mod2)
summary(mod3)
summary(mod4)

anova(mod1, mod4)
```

```{r}
plot_two_hists = function(x1, x2) {
  colvec = c(rgb(1,0,0,0.5), rgb(0,0,1,0.5))
  rangevec = c(min(x1, x2), max(x1, x2))
  hist(x1,
       breaks=seq(rangevec[1], rangevec[2], length.out=20),
       col=colvec[1],
       xlim=rangevec,
       main="Residual",
       xlab="residual"
  )
  hist(x2,
       breaks=seq(rangevec[1], rangevec[2], length.out=20),
       col=colvec[2],
       xlim=rangevec,
       add=T
  )
  legend("topright",
         legend=c(deparse(substitute(x1)), deparse(substitute(x2))),
         col=colvec,
         pch=15)
}
plot_two_hists(resid(mod1), resid(mod4))

qqnorm(resid(mod1)); qqline(resid(mod1))
qqnorm(resid(mod4)); qqline(resid(mod4))
```

Look at the example of `JohnsonJohnson`
```{r}
?JohnsonJohnson
```

The help of `JohnsonJohnson` has the example:
```{r, fig.height=8, eval = F}
JJ <- log10(JohnsonJohnson)
plot(cbind(x=JohnsonJohnson, logx=JJ),
     main="Johnson & Johnson Quarterly Earnings")
fit <- StructTS(JJ, type = "BSM")
tsdiag(fit)
sm <- tsSmooth(fit)
plot(cbind(JJ, sm[, 1], sm[, 3]-0.5), plot.type = "single",
     col = c("black", "green", "blue"))
abline(h = -0.5, col = "grey60")

monthplot(fit)
```

