---
title: "Discussion 9"
author: "Po"
date: "12/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Logistics

[Piazza](https://piazza.com/uc_davis/fall2020/sta137/home)

# Multiplicative Seasonal ARIMA Models

## Multiplicative Seasonal ARMA Models (no I)

ARMA$(p, q) \times (P, Q)_s$

For example, an ARMA$(0,1) \times (1, 0)_{12}$ is
$$
x_t = \Phi x_{t-12} + w_t + \theta w_{t-1}
$$
where $\Phi$ and $\theta$ are parameters to be fitted.

## Multiplicative Seasonal ARIMA Models

For example, an ARIMA$(0, 1, 1) \times (0, 1, 1)_{12}$ is
$$
(1 - B^{12})(1-B)x_t = (1+\Theta B^{12})(1+\theta B) w_t
$$

## Example

## Fit fit fit
Textbook library
```{r}
?astsa::sarima
```

```{r}
d = cbind(
  x = AirPassengers,
  lx = log(AirPassengers),
  dlx = diff(log(AirPassengers)),
  ddlx = diff(diff(log(AirPassengers)), 12)
)
plot(d)
```

```{r}
astsa::acf2(d[,"ddlx"], 50)
```
Fit ARIMA$(0,1,0)\times (0, 1, 0)_{12}$
```{r}
astsa::sarima(d[,"lx"], 0, 1, 0, 0, 1, 0, 12)
```

Fit ARIMA$(0,1,0)\times (0, 1, 1)_{12}$
```{r}
astsa::sarima(d[,"lx"], 0, 1, 0, 0, 1, 1, 12)
```

Fit ARIMA$(0,1,1)\times (0, 1, 0)_{12}$
```{r}
astsa::sarima(d[,"lx"], 0, 1, 1, 0, 1, 0, 12)
```
Fit ARIMA$(0,1,1)\times (0, 1, 1)_{12}$
```{r}
astsa::sarima(d[,"lx"], 0, 1, 1, 0, 1, 1, 12)
```
Fit ARIMA$(1, 1, 0)\times (1, 1, 0)_{12}$
```{r}
astsa::sarima(d[,"lx"], 1, 1, 0, 1, 1, 0, 12)
```

## Moral of the story

- Stabilize the variance with log transform if needed
- The seasonality $s$ is from common sense. Daily, weekly, Monthly, Quaterly, yearly?
- Plot the ACF, PACF of tranformed and differenced data
- Try possible ARIMA$(p, d, q) \times (P, D, Q)_{s}$. 
  - Look at the residual's ACF, Q-Qplot
  - Look at the t-test of fitted parameters and the AIC things.

